intro

### 2022-03-10 06_Paper/ER-ED/TheoreticalBackground.Rmd
Update Hyp. 5
reformulated Hyp. 5

* H5a) SVs decline with increasing effort, even after controlling for task performance measured by subjective arousal ratings, *corrugator* and *levator* activity.

>>>>

* H5a) SVs decline with increasing effort, even after controlling for task performance (decline in subjective arousal after ER), and physiological arousal (EMF *corrugator* and *levator* activity).
